On the presentation of orthogonal groups over polynomial rings

### 2019-05-02 dl-paper.tex
Minor fix

\subsection{The subgroups $P_\alpha(0)$, $P_\alpha(*)$ and their properties.} Throughout this subsection $\alpha$ denotes some fixed root of $\Phi$.
\begin{df} \label{defP0}
Denote by $P_\alpha(0)$ the subgroup of $\St(\Phi, A[X, X^{-1}])$ generated by the images of the following elements of $\St(\Phi, A[X])$ under the
 map induced by the embedding $A[X] \subseteq A[X, X^{-1}]$:
\begin{enumerate}
 \item $z_{\beta}(Xf, \xi), \beta \in \Phi \text{ such that }\alpha + \beta \in \Phi\text{ or } \alpha - \beta \in \Phi;$
 \item $z_{\beta}(f, X\xi),\ \beta \in \Phi \text{ such that }\alpha - \beta \in \Phi \cup \{0\};$
 \item $z_{\gamma}(f, \xi),\ \alpha \perp \gamma;$
 \item $x_{-\alpha}(X^2f),$
\end{enumerate}
In the above formulae and below we assume that $f \in M[X]$ and $\xi \in A[X]$. \end{df}

@@

\begin{lemma}\label{P0_conj} The subgroup $P_\alpha(0)$ is stable under conjugation by $x_\alpha(aX^{-1})$ for arbitrary $a\in A$. \end{lemma}
\begin{proof} We need to verify that the conjugate by $x_\alpha(aX^{-1})$ to every generator of $P_\alpha(0)$ lies in $P_\alpha(0)$. 
First of all, consider the case $\alpha + \beta \in \Phi$ (only possible for the generator of the first type):
\[ z_{\beta}(Xf, \xi) ^ {x_{\alpha}(aX^{-1})} = x_{\alpha} (- afg) \cdot x_{\beta+\alpha} (N_{\beta, \alpha}\cdot af)     \cdot z_{\beta}(Xf, \xi). \]
Clearly the expression in the right hand side is a product of elements of generators of type 2, 2, 1. 
Now consider the case $\alpha - \beta \in \Phi$ (possible for generators of type (1) and (2)).
\begin{align} z_{\beta}(Xf, \xi) ^ {x_{\alpha}(aX^{-1})} = &  x_{\alpha} (af\xi) \cdot x_{\alpha-\beta} (N_{\beta,-\alpha}\cdot af\xi^2) \cdot z_{\beta}(Xf, \xi), \\
z_{\beta}(f, X\xi) ^ {x_{\alpha}(aX^{-1})} = & x_{\alpha} (af\xi) \cdot x_{\alpha-\beta} (N_{\beta,-\alpha}\cdot Xf\xi^2a) \cdot z_{\beta}(f, X\xi). \end{align}
The expressions in the right-hand side are products of generators of type 2, 2, 1 and 2, 1, 2.

Let us verify the assertion for the generator of type (4).
Choose $\beta\in \Phi$ such that $\alpha+\beta \in \Phi$. 
Substituting $s = Xf$, $\eta = X$, $\xi = aX^{-1}$ and $\alpha = -\alpha - \beta$ into~\eqref{Z5} of~\cref{Zrels} we obtain that
\begin{multline} \nonumber z_{-\alpha}(X^2f, aX^{-1}) = x_{-\alpha-\beta}(\epsilon Xf) \cdot x_{-\beta}(-af) \cdot x_{\beta}(X^2 f a) \cdot x_{-\alpha}(X^2f) \cdot \\
 \cdot z_{-\alpha-\beta}(-\epsilon Xf, -\epsilon a) \cdot x_{\alpha+\beta}(-\epsilon Xf a^2) \cdot x_{\alpha}(- f a^2) \cdot z_{-\beta}(f a, -X), \end{multline}
where $\epsilon = N_{-\alpha-\beta,\beta}$. 
Clearly, the expression in the right-hand side is a product of generators of type 1, 2, 1, 1, 1, 1, 2, 2.

It remains to verify the assertion for the remaining generator $z_\alpha(f, X\xi)$ of type 2.
Substituting in~\eqref{Z5} of~\cref{Zrels} $s = -\epsilon f$, $\xi = -\epsilon \xi$, $\eta=X$ and expressing $z_\alpha(f, X\xi)$ through other terms we obtain that
\begin{multline} \nonumber z_\alpha(f, X\xi) = x_{\alpha+\beta}(\epsilon Xf) \cdot x_{\beta}(-X^2 f \xi) \cdot x_{-\beta}(f \xi) \cdot x_\alpha(f) \cdot \\ 
 \cdot z_{\alpha+\beta}(-\epsilon X f, -\epsilon \xi) \cdot z_{-\beta}(-f\xi, -X) \cdot x_{-\alpha-\beta}(-\epsilon X f \xi^2) \cdot x_{-\alpha}(-X^2 f\xi^2), \end{multline}
where $\epsilon = N_{\alpha,\beta}$.  
The factors in the right-hand side are generators of type 1, 1, 2, 2, 1, 2, 1, 4. 
It is clear, that conjugation by $x_{\alpha}(aX^{-1})$ acts trivially on the fourth factor $x_\alpha(f)$, 
while for the other factors we have already verified that their conjugates belong to $P_{\alpha}(0)$. \end{proof}

>>>>

\subsection{The subgroups $P_\alpha(0)$, $P_\alpha(*)$ and their properties.} Throughout this subsection $\alpha$ denotes some fixed root of $\Phi$.
\begin{df} \label{defP0}
Denote by $P_\alpha(0)$ the subgroup of $\St(\Phi, A[X, X^{-1}])$ generated by the images of the following elements of $\St(\Phi, A[X])$ under the
 map induced by the embedding $A[X] \subseteq A[X, X^{-1}]$:
\begin{enumerate}
 \item $z_{\beta}(Xf, \xi), \beta \in \Phi \text{ such that }\alpha + \beta \in \Phi\text{ or } \alpha - \beta \in \Phi;$
 \item $z_{\beta}(f, X\xi),\ \beta \in \Phi \text{ such that }\alpha - \beta \in \Phi \cup \{0\};$
 \item $z_{\beta}(f, \xi),\ \alpha \perp \beta;$
 \item $x_{-\alpha}(X^2f),$
\end{enumerate}
In the above formulae and below we assume that $f \in M[X]$ and $\xi \in A[X]$. \end{df}

@@

\begin{lemma}\label{P0_conj} The subgroup $P_\alpha(0)$ is stable under conjugation by $x_\alpha(aX^{-1})$ for arbitrary $a\in A$. \end{lemma}
\begin{proof} We need to verify that the conjugate by $x_\alpha(aX^{-1})$ to every generator $z_\beta(f, \xi)$ from~\cref{defP0} lies in $P_\alpha(0)$. 
First of all, consider the case $\alpha + \beta \in \Phi$, which is only possible for the generator of type 1:
\[ z_{\beta}(Xf, \xi) ^ {x_{\alpha}(aX^{-1})} = x_{\alpha} (- afg) \cdot x_{\beta+\alpha} (N_{\beta, \alpha}\cdot af)     \cdot z_{\beta}(Xf, \xi). \]
Clearly, the expression in the right hand side is a product of generators of type 2, 2, 1. 
Now consider the case $\alpha - \beta \in \Phi$, which is possible for the generators of type 1 and 2.
Computing the conjugates of these generators using~\cref{Zrels} we obtain that
\begin{align} z_{\beta}(Xf, \xi) ^ {x_{\alpha}(aX^{-1})} = &  x_{\alpha} (af\xi) \cdot x_{\alpha-\beta} (N_{\beta,-\alpha}\cdot af\xi^2) \cdot z_{\beta}(Xf, \xi), \\
z_{\beta}(f, X\xi) ^ {x_{\alpha}(aX^{-1})} = & x_{\alpha} (af\xi) \cdot x_{\alpha-\beta} (N_{\beta,-\alpha}\cdot aXf\xi^2) \cdot z_{\beta}(f, X\xi). \end{align}
The expressions in the right-hand side are products of generators of type 2, 2, 1 and 2, 1, 2.

Let us verify the assertion for the generator of type 4.
Choose $\beta\in \Phi$ such that $\alpha+\beta \in \Phi$. 
Substituting $s = Xf$, $\eta = X$, $\xi = aX^{-1}$ and $\alpha = -\alpha - \beta$ into~\eqref{Z5} of~\cref{Zrels} we obtain that
\begin{multline} \nonumber z_{-\alpha}(X^2f, aX^{-1}) = x_{-\alpha-\beta}(\epsilon Xf) \cdot x_{-\beta}(-af) \cdot x_{\beta}(aX^2 f) \cdot x_{-\alpha}(X^2f) \cdot \\
 \cdot z_{-\alpha-\beta}(-\epsilon Xf, -\epsilon a) \cdot x_{\alpha+\beta}(-\epsilon a^2 Xf) \cdot x_{\alpha}(- a^2 f) \cdot z_{-\beta}(a f, -X), \end{multline}
where $\epsilon = N_{-\alpha-\beta,\beta}$. 
Clearly, the expression in the right-hand side is a product of generators of type 1, 2, 1, 1, 1, 1, 2, 2.

It remains to verify the assertion for the remaining generator $z_\alpha(f, X\xi)$ of type 2.
Again choose $\beta$ to be any root such that $\alpha+\beta \in \Phi$.
Substituting in~\eqref{Z5} of~\cref{Zrels} $s = -\epsilon f$, $\xi = -\epsilon \xi$, $\eta=X$ and expressing $z_\alpha(f, X\xi)$ through other terms we obtain that
\begin{multline} \nonumber z_\alpha(f, X\xi) = x_{\alpha+\beta}(\epsilon Xf) \cdot x_{\beta}(-X^2 f \xi) \cdot x_{-\beta}(f \xi) \cdot x_\alpha(f) \cdot \\ 
 \cdot z_{\alpha+\beta}(-\epsilon X f, -\epsilon \xi) \cdot z_{-\beta}(-f\xi, -X) \cdot x_{-\alpha-\beta}(-\epsilon X f \xi^2) \cdot x_{-\alpha}(-X^2 f\xi^2), \end{multline}
where $\epsilon = N_{\alpha,\beta}$.  
The factors in the right-hand side are generators of type 1, 1, 2, 2, 1, 2, 1, 4. 
It is clear, that conjugation by $x_{\alpha}(aX^{-1})$ acts trivially on the fourth factor $x_\alpha(f)$, 
while for the other factors we have already verified that their conjugates belong to $P_{\alpha}(0)$. \end{proof}
